---
title: "Homework Data Viz"
author: "thidarut"
date: "2023-03-15"
output: html_document
---
#### This is YAML

## Data Visualization with Customer Shopping Dataset - Retail Sales Data
### Welcome to the shopping world of Istanbul! Our dataset contains shopping information from 10 different shopping malls between 2021 and 2023.

[kaggle](https://www.kaggle.com/datasets/mehmettahiraslan/customer-shopping-dataset)



Import library
```{r}
library(tidyverse)
library(patchwork)
library(ggplot2)
library(lubridate)
```

Load data from csv file
```{r}
cus_shop_df <- read.csv("customer_shopping_data.csv", stringsAsFactors = FALSE)
glimpse(cus_shop_df)
```


### Bar plot for The most visited shopping malls
```{r}
cus_shop_df %>%
  count(shopping_mall) %>%
  ggplot(aes(x=shopping_mall, y=n, fill=shopping_mall)) +
  geom_col() +
  theme_minimal() +
  geom_text(aes(label = n),
            position = position_stack(vjust = 0.5), 
            color = "white", size=3) +
  scale_x_discrete(guide = guide_axis(angle = 90)) +
  labs(title = "The most visited shopping malls",
    x = "Shopping malls",
    y = "Visitors count")

```










### Pie plot for shopping comparison between men and women
```{r}
f <- cus_shop_df %>%
  filter(gender == "Female") %>%
  group_by(payment_method) %>%
  summarise(price_total = sum(quantity * price)) %>%
  ggplot(aes(x="", y=price_total, fill=payment_method)) +
  geom_bar(stat="identity", col="white") +
  coord_polar("y", start=0) +
  theme_minimal() +
  geom_text(aes(label = scales::comma(price_total)), position = position_stack(vjust = 0.5), color = "gray0", size=3) +
  theme_minimal() +
  labs(title = "Shopping Girl", y= "total amount(TL)") +
  scale_fill_manual(values = c(
    "lightblue1", "lightgoldenrod1", "#FAD4D8"
  ))

m <- cus_shop_df %>%
  filter(gender == "Male") %>%
  group_by(payment_method) %>%
  summarise(price_total = sum(quantity * price)) %>%
  ggplot(aes(x="", y=price_total, fill=payment_method)) +
  geom_bar(stat="identity", col="white") +
  coord_polar("y", start=0) +
  theme_minimal() +
  geom_text(aes(label = scales::comma(price_total)), position = position_stack(vjust = 0.5), color = "white", size=3) +
  theme_minimal() +
  labs(title = "Shopping Boy", y= "total amount(TL)") +
  scale_fill_manual(values = c(
    "royalblue1", "salmon1", "palevioletred3"
  ))

f + m

```



### Horizontal barplot for product sales from 2021-2023 in Mall of Istanbul
```{r}


cus_shop_df %>%
  mutate(date_x = dmy(invoice_date), year = year(date_x)) %>%
  filter(shopping_mall == "Mall of Istanbul") %>%
  group_by(year, category) %>%
  summarise(quantity_total = sum(quantity)) %>%
  ggplot(aes(year, quantity_total, fill=category)) +
  geom_bar(stat = "identity", position = position_dodge()) +
  coord_flip()  +
  theme_bw() +
  labs(title = "Product sales from 2021-2023 in Mall of Istanbul", y= "sale") +
  scale_fill_brewer(type="qual", palette = 4)

```




### Dotplot for Sales per product By Shopping mall
```{r}
cus_shop_df %>%
  group_by(shopping_mall, category) %>%
  summarise(quantity_total = sum(quantity)) %>%
  ggplot(aes(shopping_mall, quantity_total, fill=category)) +
  geom_dotplot(binaxis='y', method="histodot") +
  scale_x_discrete(guide = guide_axis(angle = 90)) +
  theme_minimal() +
  labs(title = "Sales per product By Shopping mall") +
  scale_fill_brewer(type="qual", palette = 8)


```




### Point plot for Clothing Sales By year
```{r}

cus_shop_df %>%
  mutate(date_x = dmy(invoice_date), year = year(date_x), month_year = format(date_x,'%Y-%m')) %>%
  filter(category == "Clothing") %>%
  group_by(year, month_year, category) %>%
  summarise(quantity_total = sum(quantity)) %>%
  ggplot(aes(month_year, quantity_total)) +
  geom_point(shape=21, size=4, col = "#b3cde3", fill="#fc8d62") +
  scale_x_discrete(guide = guide_axis(angle = 90)) +
  theme_minimal() +
  labs(title = "Clothing Sales By year") +
  scale_fill_brewer(type="qual", palette = 8)


```

